### 2022-09-27 main/chapter_context.tex
try to condense intro text

\subsection{Opportunities for future Standard Models}
Problems with the Standard Model mean it needs replacing with supersymmetry
--- is currently a false statement.
Such an argument could be tempting to motivate this thesis, but the
Standard Model is actually good in its domain.
This discussion is therefore oriented towards how the Standard Model could do
better where it already works, and how that remit might expand to increase its
generality.

When `nobody knows' the answer to a riddle, the status lies between two
extremes:
many answers appear satisfactory and none is the clear best,
or no satisfactory answer is yet known.
To distinguish these two cases, we choose for them the respective labels
\emph{uncertain} and \emph{unknown}:
the model of neutrino masses is \emph{uncertain},
but the reconciliation quantum field theory with general relativity is
\emph{unknown}.

A problem with the Standard Model is that algorithms to compute its
general consequences
(where perturbative and discrete lattice methods are impractical)
are unknown.
But this is not an opportunity because it is inherent to the framework
(of quantum field theory) that all serious alternatives also use.

Before introducing supersymmetry, this section briefly review some promising
directions of change for futrue models.

>>>>

\subsection{Opportunities for future Standard Models}
Problems with the Standard Model mean it needs replacing with supersymmetry
--- is currently a false statement.
Such an argument could be tempting to motivate this thesis, but the
Standard Model is actually good in its domain.
This discussion therefore looks towards where an altered Standard Model could
go to improve what it already does, or to expand its generality.

When `nobody knows' the answer to a riddle, the status lies between two
extremes:
many answers appear satisfactory and none is the clear best,
or no satisfactory answer is yet known.
We distinguish these two cases with the respective labels
\emph{uncertain} and \emph{unknown}:
the model of neutrino masses is mostly \emph{uncertain},
but the reconciliation quantum field theory with general relativity is
mostly \emph{unknown}.

One problem with the Standard Model is that algorithms to compute its
\emph{general} consequences are unknown
where perturbative and discrete lattice methods are impractical.
But this is not an opportunity because it is inherent to the framework
of quantum field theory, which all competitive alternatives also use.
Before introducing supersymmetry, this section reviews some promising
directions of change for future models.
